Enforced Invariant Confluence

### 2018-04-21 doc/paper/sections/related_work.tex
Removed related workds section on proof assistants.

\textbf{Proof Assistants.}
Our interactive decision procedure bears resemblance to interactive proof
assistants like Coq~\cite{coq2017}, Isabelle~\cite{nipkow2002isabelle},
Agda~\cite{norell2008dependently}, and Idris~\cite{brady2013idris}. Proof
assistants guide users through the process of interactively provided a proof
that witnesses the validity of a formula. Our interactive decision procedure
guides users through the process of interactively generating a set of reachable
and unreachable points that witness the invariant-confluence of an object. An
interesting avenue for future work is to integrate an proof assistant into our
interactive decision procedure. For example, a proof assistant could verify
that a state labelled unreachable by a user is actually unreachable.

>>>>

% \textbf{Proof Assistants.}
% Our interactive decision procedure bears resemblance to interactive proof
% assistants like Coq~\cite{coq2017}, Isabelle~\cite{nipkow2002isabelle},
% Agda~\cite{norell2008dependently}, and Idris~\cite{brady2013idris}. Proof
% assistants guide users through the process of interactively provided a proof
% that witnesses the validity of a formula. Our interactive decision procedure
% guides users through the process of interactively generating a set of reachable
% and unreachable points that witness the invariant-confluence of an object. An
% interesting avenue for future work is to integrate an proof assistant into our
% interactive decision procedure. For example, a proof assistant could verify
% that a state labelled unreachable by a user is actually unreachable.
